---
title: "Alcohol vs Seat choice"
author: "Racheal Adeneye"
date: "Spring 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The median number of drinks of the back row is higher than the third quartile of the people in the front and middle rows.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

There are "bites" taking out of the boxplots. The instructor tells us that these "bites" actually represents the standard deviation - the amount of variation amongst the data. The back row drank large amounts of drinks, while the other two groups didn't drink nearly as much.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
  The Q1 of the back, front, and middle rows are all 0. The median for the front row is also 0. The Q3 of the back, front, and middle rows are 12.5, 2, and 4 respectively. The number of people in the back, front, and middle rows are 36, 40, and 89 respectively. The back row has the least amount of people. Most people are sitting in the middle row.
  
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

## Conclusions
  We will reject the null hypothesis, because the probability of getting a result like this is 0.000116, which is significantly low.
  
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

  Now that we have the box properly labeled, we can see that the 0 is only in the confidence interval between the front and the middle. However, 0 is not in the confidence interval between back and the middle nor the confidence interval between the back and the front. This tells us that the back row is statistically different from the front and middle rows. There is no statistical difference between the front and middle rows. This is a case where one category is statistically diffent from the other two that have no statistical differences.
