---
title: "Alcohol vs Seat choice"
author: "Racheal Adeneye"
date: "Spring 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The median number of drinks of the back row is higher than the third quartile of the people in the front and middle rows.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

There are "bites" taking out of the boxplots. The instructor tells us that these "bites" actually represents the standard deviation - the amount of variation amongst the data. The back row drank large amounts of drinks, while the other two groups didn't drink nearly as much.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
  The Q1 of the back, front, and middle rows are all 0. The median for the front row is also 0. The Q3 of the back, front, and middle rows are 12.5, 2, and 4 respectively. The number of people in the back, front, and middle rows are 36, 40, and 89 respectively. The back row has the least amount of people. Most people are sitting in the middle row.
  
## Inferential Tests

## Conclusions


