---
title: "Alcohol vs Seat choice"
author: "Racheal Adeneye"
date: "Spring 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The median number of drinks of the back row is higher than the third quartile of the people in the front and middle rows.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

There are "bites" taking out of the boxplots. The instructor tells us that these "bites" actually represents the standard deviation - the amount of variation amongst the data. The back row drank large amounts of drinks, while the other two groups didn't drink nearly as much.

## Numerical Summarys 

## Inferential Tests

## Conclusions


